---
title: "West Coast Text Mining"
author: "Jess Laudie"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(ggwordcloud)
library(gutenbergr)
library(textdata)
```
## Region of Choice: West Coast 

I found 10 articles related to climate change in the West Coast. All of these articles are from the Los Angelos Times newspaper and were chosen based on word count and presence of the words "climate change". 

```{r}
west_coast <- read_lines("west_coast")

west_coast <- tibble(west_coast)

west_coast$west_coast <- as.character(west_coast$west_coast)

west_coast <- west_coast %>%
  unnest_tokens(word, west_coast)%>%
  anti_join(stop_words)%>% 
  count(word, sort=TRUE)

View(west_coast)

```
This code counts how many times each word appears in the text files. Top ten most frequent words in order are climate, change, heat, energy, weather, joshua, trees, extreme, clean, and people. Time to do sentiment analysis! 

```{r}
get_sentiments('afinn')
get_sentiments('nrc')
get_sentiments('bing')

wc_sentiment_affin <- west_coast %>%
  inner_join(get_sentiments("afinn"))
View(wc_sentiment_affin)

wc_sentiment_nrc <- west_coast %>%
  inner_join(get_sentiments("nrc"))
View(wc_sentiment_nrc)

wc_sentiment_bing <- west_coast %>%
  inner_join(get_sentiments("bing"))
View(wc_sentiment_bing)

table(wc_sentiment_bing$sentiment)
## Negative sentiments (161) are nearly twice as prevalent as positive ones (81)

table(wc_sentiment_nrc$sentiment)

```
## Looking at the values of sentiment for the text file

```{r}
ggplot(data = wc_sentiment_affin, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("West Coast Climate Change Sentiment Range")+
  theme_minimal()

```

## Creating a Word Cloud

```{r}
set.seed(42)
ggplot(west_coast[1:50,], aes(label = word, size = n)
       ) +
  geom_text_wordcloud() +
  theme_minimal()
```

## Term Frequency - Inverse Document Frequency 

```{r}
wc_raw = as.tibble(read_lines("west_coast"))

data_prep <- function(x,y,z){
  i <- as_tibble(t(x))
  ii <- unite(i,"text",y:z,remove = TRUE,sep = "")
}

## Need others' data
  

```




